%%
%% This is file `./samples/longsample.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% apa7.dtx  (with options: `longsample')
%% ----------------------------------------------------------------------
%% 
%% apa7 - A LaTeX class for formatting documents in compliance with the
%% American Psychological Association's Publication Manual, 7th edition
%% 
%% Copyright (C) 2019 by Daniel A. Weiss <daniel.weiss.led at gmail.com>
%% 
%% This work may be distributed and/or modified under the
%% conditions of the LaTeX Project Public License (LPPL), either
%% version 1.3c of this license or (at your option) any later
%% version.  The latest version of this license is in the file:
%% 
%% http://www.latex-project.org/lppl.txt
%% 
%% Users may freely modify these files without permission, as long as the
%% copyright line and this statement are maintained intact.
%% 
%% This work is not endorsed by, affiliated with, or probably even known
%% by, the American Psychological Association.
%% 
%% ----------------------------------------------------------------------
%% 
\documentclass[man]{apa7}

\usepackage{lipsum}

\usepackage[american]{babel}

\usepackage{indentfirst}

\usepackage{csquotes}

\usepackage[style=apa,sortcites=true,sorting=nyt,backend=biber]{biblatex}
\DeclareLanguageMapping{american}{american-apa}
\addbibresource{Week 5.bib}



\begin{document}


\setlength{\parindent}{0.5in}
Academic integrity has begun to become an issue for individuals as well as universities and other related organizations \parencite{francisco_scholarly_2017}. A Google search identifies many options that offer dissertation and thesis consulting services \parencite{white_shadow_2016}. \textcite{francisco_scholarly_2017} defines academic integrity as

\blockquote{
an aspect of moral character and experience. It involves above all a commitment to intellectual honesty and personal responsibility for ones actions and to a range of practices that characterize responsible research conduct. Furthermore, research integrity is defined as the observance of ethical principles and professional standards for the responsible research practice. This also includes: the use of honest and verifiable methods in proposing, performing, and evaluation research. \notecite{(p. 4707)}
}

So, not only do I have to be mindful of my academic integrity as I write and complete the assignments, but I also have to be careful and maintain integrity as I start research for the dissertation part of this journey.

\setlength{\parindent}{0.5in}
There are several Bible verses that mention being a person of integrity. One such verse states: "The integrity of the upright guides them, but the unfaithful are destroyed by their duplicity" \parencite[Prov 11:3]{bible}. King Solomon had issues with integrity in his tradings with Hiram. His lack of integrity shows when he gives away cities of Israel to Hiram, something that God didn't approve of \parencite{Merida2015}. One of the reasons that I chose Liberty is because the programs do have a Biblical component so I believe we must maintain an even higher standard in our work. 

\setlength{\parindent}{0.5in}
I want to truly know what it means to have Godly wisdom and integrity. While I may not always win, if I have integrity I will try to follow God's will is my life. "I know that you are pleased with me, for my enemy does not triumph over me. Because of my integrity you uphold me and set me in your presence forever" \parencite[Psalm 41:11-2]{bible}.  

\setlength{\parindent}{0.5in}
According to \textcite{white_shadow_2016}, the lack of academic integrity can not only damage a student's academic career but it can also damage their future professional career and reputation. 

\blockquote{
By claiming authorship of the thesis or dissertation, the degree can be characterized as received on the basis of academic fraud. Sanctioning external help as anything other than plagiarism sets a dangerous precedent for later career patterns of similar unethical behavior. \parencite[p. 4]{white_shadow_2016}
}

As the quote suggests, if one is prone to slips of integrity in your academic career then who is say that a person won't do the same thing in their professional career. Personally, I want to run as far away from anything that appears to lack integrity.
I have developed a few examples of how I can try to maintain academic integrity:

\begin{itemize}
  \item I will plan ahead and use good time management.    
  \item I won't wait until the last minute to do an assignment. Being rushed can led to sloppiness and laziness which can lead to plagiarism.
  \item I will make sure that I understand the assignment and its requirements.
  \item I will use some sort of citation manager to keep track of references. I'm using Zotero.
\end{itemize}
I believe that by following these four items I will be able to maintain my integrity in both the DSL program and in my future endeavors.

\printbibliography


\end{document}

%% 
%% Copyright (C) 2019 by Daniel A. Weiss <daniel.weiss.led at gmail.com>
%% 
%% This work may be distributed and/or modified under the
%% conditions of the LaTeX Project Public License (LPPL), either
%% version 1.3c of this license or (at your option) any later
%% version.  The latest version of this license is in the file:
%% 
%% http://www.latex-project.org/lppl.txt
%% 
%% Users may freely modify these files without permission, as long as the
%% copyright line and this statement are maintained intact.
%% 
%% This work is not endorsed by, affiliated with, or probably even known
%% by, the American Psychological Association.
%% 
%% This work is "maintained" (as per LPPL maintenance status) by
%% Daniel A. Weiss.
%% 
%% This work consists of the file  apa7.dtx
%% and the derived files           apa7.ins,
%%                                 apa7.cls,
%%                                 apa7.pdf,
%%                                 README,
%%                                 APA7american.txt,
%%                                 APA7british.txt,
%%                                 APA7dutch.txt,
%%                                 APA7english.txt,
%%                                 APA7german.txt,
%%                                 APA7ngerman.txt,
%%                                 APA7greek.txt,
%%                                 APA7czech.txt,
%%                                 APA7turkish.txt,
%%                                 APA7endfloat.cfg,
%%                                 Figure1.pdf,
%%                                 shortsample.tex,
%%                                 longsample.tex, and
%%                                 bibliography.bib.
%% 
%%
%% End of file `./samples/longsample.tex'.
